A cross-benchmark comparison of Learning to Rank methods

### 2014-05-16 cikm_paper/paper.tex
ndcg10 in meestertabel :)
map in meestertabel :)
meestertabel af :)
andere tabellen weg

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{Bibliography}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
\section{Raw Data for NDCG@3 Comparison}
\label{app:norm_winnum_NDCG3}

\begin{table*}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.34862385 & 12 \\ 
AdaRank-NDCG & 0.30733945 & 12 \\ 
ApproxNDCG & 0.79487179 & 1 \\ 
BagBoo & 0.84782609 & 2 \\ 
BL-MART & 0.95238095 & 2 \\ 
BoltzRank-Pair & 0.83333333 & 4 \\ 
BoltzRank-Single & 0.75490196 & 4 \\ 
BT & 0.72727273 & 3 \\ 
CoList & 1.00000000 & 1 \\ 
DCMP & 0.54591837 & 9 \\ 
EnergyNDCG & 0.36363636 & 2 \\ 
FBPCRank & 0.41463415 & 3 \\ 
FenchelRank & 0.77419355 & 5 \\ 
FocusedBoost & 0.37500000 & 2 \\ 
FocusedNet & 0.45833333 & 2 \\ 
FocusedSVM & 0.25000000 & 2 \\ 
FRank & 0.30845771 & 11 \\ 
FSMRank & 0.83333333 & 4 \\ 
FSMSVM & 0.22916667 & 4 \\ 
GAS-E & 0.37500000 & 4 \\ 
GPRank & 0.87096774 & 3 \\ 
GroupCE & 0.73118280 & 3 \\ 
GroupMLE & 0.52688172 & 3 \\ 
IntervalRank & 0.58974359 & 1 \\ 
IPRank & 0.93548387 & 3 \\ 
KL-CRF & 0.59459459 & 2 \\ 
LambdaMART & 0.57142857 & 2 \\ 
LambdaNeuralRank & 1.00000000 & 1 \\ 
LambdaRank & 0.20000000 & 1 \\ 
LARF & 0.98924731 & 3 \\ 
Linear Regression & 0.07142857 & 9 \\ 
ListMLE & 0.00000000 & 1 \\ 
ListNet & 0.44954128 & 12 \\ 
ListReg & 0.73118280 & 3 \\ 
LRUF & 0.98230088 & 4 \\ 
MHR & 0.75000000 & 1 \\ 
NewLoss & 0.51612903 & 3 \\ 
OWPC & 0.65000000 & 6 \\ 
PERF-MAP & 0.38938053 & 4 \\ 
RankBoost & 0.32110092 & 12 \\ 
RankELM (pairwise) & 0.61538462 & 1 \\ 
RankELM (pointwise) & 0.69230769 & 1 \\ 
RankNet & 0.18867925 & 1 \\ 
RankSVM & 0.30097087 & 12 \\ 
RankSVM-Primal & 0.39204545 & 8 \\ 
RankSVM-Struct & 0.35204082 & 9 \\ 
REG-SHF-SDCG & 0.38461538 & 1 \\ 
Ridge Regression & 0.40880503 & 7 \\ 
RSRank & 0.57291667 & 4 \\ 
SmoothRank & 0.60377358 & 7 \\ 
SoftRank & 0.23076923 & 1 \\ 
SortNet & 0.25000000 & 2 \\ 
SparseRank & 0.82242991 & 4 \\ 
SVMMAP & 0.28930818 & 7 \\ 
TGRank & 0.54166667 & 4 \\ 
TM & 0.59090909 & 3 \\
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on NDCG@3}
\label{tab:raw_data_norm_winnum_NDCG3}
\end{table*}

\section{Raw Data for NDCG@5 Comparison}
\label{app:norm_winnum_NDCG5}

\begin{table*}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.3883929 & 12 \\ 
AdaRank-NDCG & 0.3258929 & 12 \\ 
ApproxNDCG & 0.7500000 & 1 \\ 
BagBoo & 0.8400000 & 1 \\ 
BL-MART & 0.7200000 & 1 \\ 
BoltzRank-Pair & 0.8349515 & 4 \\ 
BoltzRank-Single & 0.7184466 & 4 \\ 
BT & 0.7878788 & 3 \\ 
C-CRF & 0.9500000 & 2 \\ 
DCMP & 0.5078534 & 9 \\ 
EnergyNDCG & 0.3777778 & 2 \\ 
FBPCRank & 0.5529412 & 3 \\ 
FenchelRank & 0.7500000 & 5 \\ 
FocusedBoost & 0.4545455 & 2 \\ 
FocusedNet & 0.6363636 & 2 \\ 
FocusedSVM & 0.2727273 & 2 \\ 
FPRank & 0.9000000 & 1 \\ 
FRank & 0.2849462 & 10 \\ 
FSMRank & 0.8775510 & 4 \\ 
FSMSVM & 0.4081633 & 4 \\ 
GAS-E & 0.4693878 & 4 \\ 
GPRank & 0.7252747 & 3 \\ 
IntervalRank & 0.3750000 & 1 \\ 
IPRank & 0.8131868 & 3 \\ 
Kernel-PCA & 0.2857143 & 3 \\ 
KL-CRF & 0.5789474 & 2 \\ 
LambdaNeuralRank & 1.0000000 & 1 \\ 
LambdaRank & 0.2000000 & 1 \\ 
LARF & 0.9890110 & 3 \\ 
Linear Regression & 0.1099476 & 9 \\ 
ListNet & 0.4910714 & 12 \\ 
ListReg & 0.6923077 & 3 \\ 
LRUF & 0.9816514 & 4 \\ 
MHR & 0.6000000 & 1 \\ 
NewLoss & 0.4285714 & 3 \\ 
PERF-MAP & 0.2660550 & 4 \\ 
Q.D.KNN & 0.3205128 & 3 \\ 
RankAggNDCG & 0.5000000 & 3 \\ 
RankBoost & 0.2794118 & 10 \\ 
RankDE & 0.5384615 & 1 \\ 
RankELM (pairwise) & 0.6500000 & 1 \\ 
RankELM (pointwise) & 0.7000000 & 1 \\ 
RankNet & 0.2857143 & 3 \\ 
Rank-PMBGP & 0.7692308 & 1 \\ 
RankSVM & 0.3612565 & 11 \\ 
RankSVM-Primal & 0.4508671 & 8 \\ 
RankSVM-Struct & 0.4136126 & 9 \\ 
RCP & 0.5757576 & 3 \\ 
REG-SHF-SDCG & 0.4500000 & 1 \\ 
Ridge Regression & 0.3333333 & 7 \\ 
RSRank & 0.5306122 & 4 \\ 
SmoothRank & 0.6339869 & 7 \\ 
SoftRank & 0.2750000 & 1 \\ 
SortNet & 0.5147059 & 4 \\ 
SparseRank & 0.8173077 & 4 \\ 
SVD-RankBoost & 0.2727273 & 3 \\ 
SVMMAP & 0.3801170 & 8 \\ 
SwarmRank & 0.1538462 & 1 \\ 
TGRank & 0.6122449 & 4 \\ 
TM & 0.7575758 & 3 \\ 
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on NDCG@5}
\label{tab:raw_data_norm_winnum_NDCG5}
\end{table*}

\section{Raw Data for NDCG@10 Comparison}
\label{app:norm_winnum_NDCG10}

\begin{table*}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.36480687 & 13 \\ 
AdaRank-NDCG & 0.31578947 & 16 \\ 
ADMM & 0.44444444 & 1 \\ 
ApproxNDCG & 0.86111111 & 1 \\ 
Best Single Feature & 0.16149068 & 8 \\ 
CA & 0.65217391 & 4 \\ 
CoList & 0.16666667 & 1 \\ 
Consistent-RankCosine & 0.76923077 & 2 \\ 
DCMP & 0.58883249 & 9 \\ 
DirectRank & 0.92307692 & 2 \\ 
EnergyNDCG & 0.41463415 & 2 \\ 
FenchelRank & 0.76229508 & 5 \\ 
FocusedBoost & 0.68627451 & 2 \\ 
FocusedNet & 0.86274510 & 2 \\ 
FocusedSVM & 0.60784314 & 2 \\ 
FRank & 0.30288462 & 11 \\ 
FSMRank & 0.86206897 & 5 \\ 
FSMSVM & 0.54255319 & 4 \\ 
GAS-E & 0.45744681 & 4 \\ 
GP & 0.66666667 & 2 \\ 
GPRank & 0.65909091 & 3 \\ 
GRankRLS & 0.28947368 & 2 \\ 
GroupCE & 0.72727273 & 3 \\ 
GroupMLE & 0.62500000 & 3 \\ 
IPRank & 0.79545455 & 3 \\ 
LAC-MR-OR & 0.66666667 & 2 \\ 
LambdaMART & 1.00000000 & 1 \\ 
LambdaNeuralRank & 1.00000000 & 1 \\ 
LambdaRank & 0.57142857 & 2 \\ 
LARF & 0.98863636 & 3 \\ 
Linear Regression & 0.08287293 & 8 \\ 
ListMLE & 0.02127660 & 4 \\ 
ListNet & 0.59821429 & 12 \\ 
LRUF & 0.98181818 & 4 \\ 
MHR & 0.62500000 & 1 \\ 
NewLoss & 0.39772727 & 3 \\ 
PERF-MAP & 0.20000000 & 4 \\ 
Q.D.KNN & 0.50000000 & 3 \\ 
RandomForest & 0.42236025 & 8 \\ 
RankAggNDCG & 0.87837838 & 3 \\ 
RankBoost & 0.39357430 & 17 \\ 
RankDE & 0.18181818 & 1 \\ 
RankELM (pairwise) & 0.69444444 & 1 \\ 
RankELM (pointwise) & 0.80555556 & 1 \\ 
RankNet & 0.59154930 & 5 \\ 
Rank-PMBGP & 0.27272727 & 1 \\ 
RankRLS & 0.36842105 & 2 \\ 
RankSVM & 0.44957983 & 17 \\ 
RankSVM-Primal & 0.45911950 & 7 \\ 
RankSVM-Struct & 0.44670051 & 9 \\ 
RCP & 0.74074074 & 3 \\ 
Ridge Regression & 0.36477987 & 7 \\ 
RSRank & 0.62765957 & 4 \\ 
SmoothGrad & 0.38461538 & 2 \\ 
SmoothRank & 0.64150943 & 7 \\ 
SoftRank & 0.61111111 & 1 \\ 
SortNet & 0.56666667 & 4 \\ 
SparseRank & 0.79439252 & 4 \\ 
SVD-RankBoost & 0.55555556 & 3 \\ 
SVMMAP & 0.35911602 & 8 \\ 
SwarmRank & 0.09090909 & 1 \\ 
TGRank & 0.50000000 & 4 \\
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on NDCG@10}
\label{tab:raw_data_norm_winnum_NDCG10}
\end{table*}

\section{Raw Data for MAP Comparison}
\label{app:norm_winnum_map}

\begin{table*}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.320610687 & 12 \\ 
AdaRank-NDCG & 0.286259542 & 12 \\ 
ApproxAP & 0.500000000 & 2 \\ 
BagBoo & 0.654545455 & 2 \\ 
BL-MART & 0.803571429 & 3 \\ 
BoltzRank-Pair & 0.580419580 & 5 \\ 
BoltzRank-Single & 0.433566434 & 5 \\ 
BT & 0.750000000 & 3 \\ 
CCRank & 0.615384615 & 2 \\ 
FenchelRank & 0.641791045 & 5 \\ 
FRank & 0.262295082 & 11 \\ 
FSMRank & 0.578947368 & 7 \\ 
FSMSVM & 0.350000000 & 4 \\ 
GAS-E & 0.410000000 & 4 \\ 
GP & 0.500000000 & 2 \\ 
GPRank & 0.817307692 & 3 \\ 
GroupCE & 0.721153846 & 3 \\ 
GroupMLE & 0.653846154 & 3 \\ 
IntervalRank & 0.315789474 & 1 \\ 
IPRank & 0.851351351 & 6 \\ 
KeepRank & 0.538461538 & 3 \\ 
LAC-MR-OR & 0.764192140 & 12 \\ 
LambdaMART & 0.678571429 & 3 \\ 
LARF & 0.980769231 & 3 \\ 
Linear Regression & 0.065000000 & 8 \\ 
ListMLE & 0.009615385 & 3 \\ 
ListNet & 0.450381679 & 12 \\ 
ListReg & 0.432692308 & 3 \\ 
LRUF & 0.968000000 & 4 \\ 
MCP & 0.571428571 & 2 \\ 
MHR & 0.000000000 & 1 \\ 
MultiStageBoost & 0.136363636 & 2 \\ 
OWPC & 0.624113475 & 6 \\ 
PERF-MAP & 0.768000000 & 4 \\ 
PermuRank & 0.409090909 & 3 \\ 
Q.D.KNN & 0.558441558 & 3 \\ 
RandomForest & 0.438888889 & 8 \\ 
RankAggNDCG & 0.792207792 & 3 \\ 
RankBoost & 0.313432836 & 14 \\ 
RankCSA & 0.916666667 & 2 \\ 
RankDE & 1.000000000 & 1 \\ 
RankELM (pairwise) & 0.514285714 & 2 \\ 
RankELM (pointwise) & 0.542857143 & 2 \\ 
RankMGP & 0.222222222 & 1 \\ 
Rank-PMBGP & 0.875000000 & 1 \\ 
RankSVM & 0.340000000 & 13 \\ 
RankSVM-Primal & 0.351955307 & 7 \\ 
RankSVM-Struct & 0.362385321 & 9 \\ 
RCP & 0.363636364 & 3 \\ 
REF-SHF-SDCG & 0.657894737 & 1 \\ 
RE-QR & 0.865921788 & 7 \\ 
Ridge Regression & 0.290502793 & 7 \\ 
RSRank & 0.660000000 & 4 \\ 
SmoothRank & 0.530726257 & 7 \\ 
SortNet & 0.500000000 & 2 \\ 
SVD-RankBoost & 0.568181818 & 3 \\ 
SVMMAP & 0.349775785 & 10 \\ 
SwarmRank & 0.125000000 & 1 \\ 
TGRank & 0.460000000 & 4 \\ 
TM & 0.613636364 & 3 \\ 
VFLR & 0.974358974 & 2 \\
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on MAP}
\label{tab:raw_data_norm_winnum_map}
\end{table*}

\section{Raw Data on Normalised Winning Number for cross-comparison}
\label{app:norm_winnum_all}

@@

\begin{longtable}{@{}rrrrrrrrrrrrrrrrr@{}}\toprule

@@

ADMM & & && & && & && & && & & \\
ApproxAP & & && & && & && & && & & \\
ApproxNDCG & & && & && & && & && & & \\
BagBoo & & && & && & && & && & & \\
Best Single Feature & & && & && & && & && & & \\
BL-MART & & && & && & && & && & & \\
BoltzRank-Pair & & && & && & && & && & & \\
BoltzRank-Single & & && & && & && & && & & \\
BT & & && & && & && & && & & \\
C-CRF & & && & && & && & && & & \\
CA & & && & && & && & && & & \\
CCRank & & && & && & && & && & & \\
CoList & & && & && & && & && & & \\
Consistent-RankCosine & & && & && & && & && & & \\
DCMP & & && & && & && & && & & \\
DirectRank & & && & && & && & && & & \\
EnergyNDCG & & && & && & && & && & & \\
FBPCRank & & && & && & && & && & & \\
FenchelRank & & && & && & && & && & & \\
FocusedBoost & & && & && & && & && & & \\
FocusedNet & & && & && & && & && & & \\
FocusedSVM & & && & && & && & && & & \\
FP-Rank & & && & && & && & && & & \\
FRank & & && & && & && & && & & \\
FSMRank & & && & && & && & && & & \\
FSM$^{SVM}$ & & && & && & && & && & & \\
GAS-E & & && & && & && & && & & \\
GP & & && & && & && & && & & \\
GPRank & & && & && & && & && & & \\
GRankRLS & & && & && & && & && & & \\
GroupCE & & && & && & && & && & & \\
GroupMLE & & && & && & && & && & & \\
IntervalRank & & && & && & && & && & & \\
IPRank & & && & && & && & && & & \\
KeepRank & & && & && & && & && & & \\
Kernel-PCA RankBoost & & && & && & && & && & & \\
KL-CRF & & && & && & && & && & & \\
LAC-MR-OR & & && & && & && & && & & \\
LambdaMART & & && & && & && & && & & \\
LambdaNeuralRank & & && & && & && & && & & \\
LambdaRank & & && & && & && & && & & \\
LARF & & && & && & && & && & & \\
Linear Regression & & && & && & && & && & & \\
ListMLE & & && & && & && & && & & \\
ListNet & & && & && & && & && & & \\
ListReg & & && & && & && & && & & \\
LRUF & & && & && & && & && & & \\
MCP & & && & && & && & && & & \\
MHR & & && & && & && & && & & \\
MultiStageBoost & & && & && & && & && & & \\
NewLoss & & && & && & && & && & & \\
OWPC & & && & && & && & && & & \\
PERF-MAP & & && & && & && & && & & \\
PermuRank & & && & && & && & && & & \\
Q.D.KNN & & && & && & && & && & & \\
RandomForest & & && & && & && & && & & \\
Rank-PMBGP & & && & && & && & && & & \\
RankAggNDCG & & && & && & && & && & & \\
RankBoost & & && & && & && & && & & \\
RankCSA & & && & && & && & && & & \\
RankDE & & && & && & && & && & & \\
RankELM (pairwise) & & && & && & && & && & & \\
RankELM (pointwise) & & && & && & && & && & & \\
RankMGP & & && & && & && & && & & \\
RankNet & & && & && & && & && & & \\
RankRLS & & && & && & && & && & & \\
RankSVM & & && & && & && & && & & \\
RankSVM-Primal & & && & && & && & && & & \\
RankSVM-Struct & & && & && & && & && & & \\
RCP & & && & && & && & && & & \\
RE-QR & & && & && & && & && & & \\
REG-SHG-SDCG & & && & && & && & && & & \\
Ridge Regression & & && & && & && & && & & \\
RSRank & & && & && & && & && & & \\
SmoothGrad & & && & && & && & && & & \\
SmoothRank & & && & && & && & && & & \\
SoftRank & & && & && & && & && & & \\
SparseRank & & && & && & && & && & & \\
SVD-RankBoost & & && & && & && & && & & \\
SVM$^{MAP}$ & & && & && & && & && & & \\
SwarmRank & & && & && & && & && & & \\
TGRank & & && & && & && & && & & \\
TM & & && & && & && & && & & \\
VFLR & & && & && & && & && & & \\

>>>>

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{Bibliography}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
\section{Cross-Comparison Raw Data}
\label{app:raw_data}

@@

\begin{longtable}{@{}lrrrrrrrrrrrrrrrr@{}}\toprule

@@

ADMM & - & - && - & - && 0.4444 & 1 && - & - && 4 & 9 & 0.4444 \\
ApproxAP & - & - && - & - && - & - && 0.5000 & 2 && 33 & 66 & 0.5000 \\
ApproxNDCG & 0.7949 & 1 && 0.7500 & 1 && 0.8611 & 1 && - & - && 92 & 115 & 0.8000 \\
BagBoo & 0.8478 & 2 && 0.8400 & 1 && - & - && 0.6545 & 2 && 96 & 126 & 0.7619 \\
Best Single Feature & - & - && - & - && 0.1615 & 8 && - & - && 26 & 161 & 0.1615 \\
BL-MART & 0.9524 & 2 && 0.7200 & 1 && - & - && 0.8036 & 3 && 83 & 102 & 0.8137 \\
BoltzRank-Pair & 0.8333 & 4 && 0.8350 & 4 && - & - && 0.5804 & 5 && 254 & 348 & 0.7299 \\
BoltzRank-Single & 0.7549 & 4 && 0.7184 & 4 && - & - && 0.4336 & 5 && 213 & 348 & 0.6121 \\
BT & 0.7273 & 3 && 0.7879 & 3 && - & - && 0.7500 & 3 && 75 & 99 & 0.7576 \\
C-CRF & - & - && 0.9500 & 2 && - & - && - & - && 19 & 20 & 0.9500 \\
CA & - & - && - & - && 0.6522 & 4 && - & - && 15 & 23 & 0.6522 \\
CCRank & - & - && - & - && - & - && 0.6154 & 2 && 24 & 39 & 0.6154 \\
CoList & 1.0000 & 1 && - & - && 0.1667 & 1 && - & - && 2 & 7 & 0.2857 \\
Consistent-RankCosine & - & - && - & - && 0.7692 & 2 && - & - && 10 & 13 & 0.7692 \\
DCMP & 0.5459 & 9 && 0.5079 & 9 && 0.5888 & 9 && - & - && 320 & 584 & 0.5479 \\
DirectRank & - & - && - & - && 0.9231 & 2 && - & - && 12 & 13 & 0.9231 \\
EnergyNDCG & 0.3636 & 2 && 0.3778 & 2 && 0.4146 & 2 && - & - && 50 & 130 & 0.3846 \\
FBPCRank & 0.4146 & 3 && 0.5529 & 3 && - & - && - & - && 81 & 167 & 0.4850 \\
FenchelRank & 0.7742 & 5 && 0.7500 & 5 && 0.7623 & 5 && 0.6418 & 5 && 368 & 504 & 0.7302 \\
FocusedBoost & 0.3750 & 2 && 0.4545 & 2 && 0.6863 & 2 && - & - && 73 & 143 & 0.5105 \\
FocusedNet & 0.4583 & 2 && 0.6364 & 2 && 0.8627 & 2 && - & - && 94 & 143 & 0.6573 \\
FocusedSVM & 0.2500 & 2 && 0.2727 & 2 && 0.6078 & 2 && - & - && 55 & 143 & 0.3846 \\
FP-Rank & - & - && 0.9000 & 1 && - & - && - & - && 18 & 20 & 0.9000 \\
FRank & 0.3085 & 11 && 0.2849 & 10 && 0.3029 & 11 && 0.2623 & 11 && 242 & 839 & 0.2884 \\
FSMRank & 0.8333 & 4 && 0.8776 & 4 && 0.8621 & 5 && 0.5789 & 7 && 365 & 481 & 0.7588 \\
FSM$^{SVM}$ & 0.2292 & 2 && 0.4082 & 4 && 0.5426 & 4 && 0.3500 & 4 && 148 & 388 & 0.3814 \\
GAS-E & 0.3750 & 4 && 0.4694 & 4 && 0.4574 & 4 && 0.4100 & 4 && 166 & 388 & 0.4278 \\
GP & - & - && - & - && 0.6667 & 2 && 0.5000 & 2 && 7 & 12 & 0.5833 \\
GPRank & 0.8710 & 3 && 0.7253 & 3 && 0.6591 & 3 && 0.8173 & 3 && 290 & 376 & 0.7713 \\
GRankRLS & - & - && - & - && 0.2895 & 2 && - & - && 11 & 38 & 0.2895 \\
GroupCE & 0.7312 & 3 && - & - && 0.7273 & 3 && 0.7212 & 3 && 207 & 285 & 0.7263 \\
GroupMLE & 0.5269 & 3 && - & - && 0.6250 & 3 && 0.6538 & 3 && 172 & 285 & 0.6035 \\
IntervalRank & 0.5897 & 1 && 0.3750 & 1 && - & - && 0.3158 & 1 && 50 & 117 & 0.4274 \\
IPRank & 0.9355 & 3 && 0.8132 & 3 && 0.7955 & 3 && 0.8514 & 6 && 357 & 420 & 0.8500 \\
KeepRank & - & - && - & - && - & - && 0.5385 & 3 && 56 & 104 & 0.5385 \\
KL-CRF & 0.5946 & 2 && 0.5789 & 2 && - & - && - & - && 44 & 75 & 0.5867 \\
LAC-MR-OR & - & - && - & - && 0.6667 & 2 && 0.7642 & 12 && 179 & 235 & 0.7617 \\
LambdaMART & 0.5714 & 2 && - & - && 1.0000 & 1 && 0.6786 & 3 && 54 & 81 & 0.6667 \\
LambdaNeuralRank & 1.0000 & 1 && 1.0000 & 1 && 1.0000 & 1 && - & - && 15 & 15 & 1.0000 \\
LambdaRank & 0.2000 & 1 && 0.2000 & 1 && 0.5714 & 2 && - & - && 10 & 24 & 0.4167 \\
LARF & 0.9892 & 3 && 0.9890 & 3 && 0.9886 & 3 && 0.9808 & 3 && 371 & 376 & 0.9867 \\
Linear Regression & 0.0714 & 9 && 0.1099 & 9 && 0.0829 & 8 && 0.0650 & 8 && 63 & 761 & 0.0828 \\
ListMLE & 0.0000 & 1 && - & - && 0.0213 & 4 && 0.00962 & 3 && 3 & 199 & 0.0151 \\
ListNet & 0.4495 & 12 && 0.4911 & 12 && 0.5982 & 12 && 0.4504 & 12 && 460 & 928 & 0.496 \\
ListReg & 0.7312 & 3 && 0.6923 & 3 && - & - && 0.4327 & 3 && 176 & 288 & 0.6111 \\
LRUF & 0.9823 & 4 && 0.9817 & 4 && 0.9818 & 4 && 0.9680 & 4 && 447 & 457 & 0.9781 \\
MCP & - & - && - & - && - & - && 0.5714 & 2 && 40 & 70 & 0.5714 \\
MHR & 0.7500 & 1 && 0.6000 & 1 && 0.6250 & 1 && 0.0000 & 1 && 17 & 41 & 0.5714 \\
MultiStageBoost & - & - && - & - && - & - && 0.1364 & 2 && 6 & 44 & 0.1364 \\
NewLoss & 0.5161 & 3 && 0.4286 & 3 && 0.3977 & 3 && - & - && 122 & 272 & 0.4485 \\
OWPC & 0.6500 & 6 && - & - && - & - && 0.6241 & 6 && 166 & 261 & 0.6360 \\
PERF-MAP & 0.3894 & 4 && 0.2661 & 4 && 0.2000 & 4 && 0.7680 & 4 && 191 & 457 & 0.4179 \\
PermuRank & - & - && - & - && - & - && 0.4091 & 3 && 18 & 44 & 0.4091 \\
Q.D.KNN & - & - && 0.3205 & 3 && 0.5000 & 3 && 0.5584 & 3 && 105 & 229 & 0.4585 \\
RandomForest & - & - && - & - && 0.4224 & 8 && 0.4389 & 8 && 147 & 341 & 0.4311 \\
Rank-PMBGP & - & - && 0.7692 & 1 && 0.2727 & 1 && 0.8750 & 1 && 24 & 40 & 0.6750 \\
RankAggNDCG & - & - && 0.5000 & 3 && 0.8784 & 3 && 0.7922 & 3 && 165 & 229 & 0.7205 \\
RankBoost & 0.3211 & 12 && 0.2794 & 10 && 0.3936 & 17 && 0.3134 & 14 && 309 & 939 & 0.3291 \\
RankBoost (Kernel-PCA) & - & - && 0.2857 & 3 && - & - && - & - && 26 & 91 & 0.2857 \\
RankBoost (SVD) & - & - && 0.2727 & 3 && 0.5556 & 3 && 0.5682 & 3 && 49 & 104 & 0.4712 \\
RankCSA & - & - && - & - && - & - && 0.9167 & 2 && 33 & 36 & 0.9167 \\
RankDE & - & - && 0.5385 & 1 && 0.1818 & 1 && 1.0000 & 1 && 25 & 40 & 0.6250 \\
RankELM (pairwise) & 0.6154 & 1 && 0.6500 & 1 && 0.6944 & 1 && 0.5143 & 2 && 111 & 185 & 0.6000 \\
RankELM (pointwise) & 0.6923 & 1 && 0.7000 & 1 && 0.8056 & 1 && 0.5429 & 2 && 122 & 185 & 0.6595 \\
RankMGP & - & - && - & - && - & - && 0.2222 & 1 && 4 & 18 & 0.2222 \\
RankNet & 0.1887 & 1 && 0.2857 & 3 && 0.5915 & 5 && - & - && 66 & 173 & 0.3815 \\
RankRLS & - & - && - & - && 0.3684 & 2 && - & - && 14 & 38 & 0.3684 \\
RankSVM & 0.3010 & 12 && 0.3613 & 11 && 0.4496 & 17 && 0.3400 & 13 && 323 & 885 & 0.3650 \\
RankSVM-Primal & 0.3920 & 8 && 0.4509 & 8 && 0.4591 & 7 && 0.3520 & 7 && 283 & 687 & 0.4119 \\
RankSVM-Struct & 0.3520 & 9 && 0.4136 & 9 && 0.4467 & 9 && 0.3624 & 9 && 315 & 793 & 0.3928 \\
RCP & - & - && 0.5758 & 3 && 0.7407 & 3 && 0.3636 & 3 && 55 & 104 & 0.5288 \\
RE-QR & - & - && - & - && - & - && 0.8659 & 7 && 155 & 179 & 0.8659 \\
REG-SHG-SDCG & 0.3846 & 1 && 0.4500 & 1 && - & - && 0.6579 & 1 && 58 & 117 & 0.4957 \\
Ridge Regression & 0.4088 & 7 && 0.3333 & 7 && 0.3648 & 7 && 0.2905 & 7 && 226 & 650 & 0.3477 \\
RSRank & 0.5729 & 4 && 0.5306 & 4 && 0.6277 & 4 && 0.6600 & 4 && 232 & 388 & 0.5979 \\
SmoothGrad & - & - && - & - && 0.3846 & 2 && - & - && 5 & 13 & 0.3846 \\
SmoothRank & 0.6038 & 7 && 0.6340 & 7 && 0.6415 & 7 && 0.5307 & 7 && 390 & 650 & 0.6000 \\
SoftRank & 0.2308 & 1 && 0.2750 & 1 && 0.6111 & 1 && - & - && 42 & 115 & 0.3652 \\
SortNet & 0.2500 & 2 && 0.5147 & 4 && 0.5667 & 4 && 0.5000 & 2 && 113 & 238 & 0.4748 \\
SparseRank & 0.8224 & 4 && 0.8173 & 4 && 0.7944 & 4 && - & - && 258 & 318 & 0.8113 \\
SVM$^{MAP}$ & 0.2893 & 7 && 0.3801 & 8 && 0.3591 & 8 && 0.3498 & 10 && 254 & 734 & 0.3460 \\
SwarmRank & - & - && 0.1538 & 1 && 0.0909 & 1 && 0.1250 & 1 && 5 & 40 & 0.1250 \\
TGRank & 0.5417 & 4 && 0.6122 & 4 && 0.5000 & 4 && 0.4600 & 4 && 205 & 388 & 0.5284 \\
TM & 0.5909 & 3 && 0.7576 & 3 && - & - && 0.6136 & 3 && 65 & 99 & 0.6566 \\
VFLR & - & - && - & - && - & - && 0.9744 & 2 && 38 & 39 & 0.9744 \\
